### 2023-02-28 observingCarbonCycle.qmd
update

![$e-ratio$ estimations obtained with different types of models: empirical models (a, b), food-web models (c, d) and data-assimilated models (e, f). Note that the export value computed by @Laws2011-nw (9 Pg C y$^{-1}$) was recomputed by @Siegel2022-wd (6.9 Pg C y$^{-1}$), therefore the $e-ratio$ map presented here might not be representative of the one we would have got with with the initial export value. Figure taken from @Siegel2022-wd.](image/ObservingCarbonCycle/export_ratio.jpeg){#fig-export-ratios}

@@

@Henson2011-mt and @Laws2011-nw (panels a and b in @fig-export-ratios) are both empirical models. @Henson2011-mt parameterized the $e-ratio$ as a decreasing function of SST (derived from satellite observations, see @fig-bgc-models) tuned on a compilation of $^{234}Th$-derived export measurement (see @sec-historical-measurements) for a total export estimated at 5 Pg C y$^{-1}$. @Laws2011-nw modelled the $e-ratio$ as a decreasing linear function of SST and a power-law function of NPP whose parameters were determined using particle export estimates based on estimates of new production (nitrogen-based) and $^{234}Th$ and sediment trap export flux data compiled by @Dunne2005-an. They estimated a total export of 9 Pg C y$^{-1}$.

@Siegel2014-wg and @Archibald2019-dj (panels c and d in @fig-export-ratios) are both food-web models (see Information Box 3). @Siegel2014-wg used a mechanistic approach using satellite observations (NPP, PSS and phytoplankton carbon concentrations, see also @fig-bgc-models) to estimate the export of the BGP (6 Pg C y$^{-1}$). @Archibald2019-dj added a new module to the model of @Siegel2014-wg in order to incorporate the diel vertical migration of zooplankton for a total export of 6.5 Pg C y$^{-1}$.

@@

A simple food-web model is the NPZD model, which consists of four state variables: Nutrient (DIN), Phytoplankton (PHYTO), Zooplankton (ZOO) and DETRITUS. The arrows represent the flows (or interactions) between the state variables (e.g. f1 represents the DIN uptake by PHYTO, f2 represents the grazing of PHYTO by ZOO, etc.), describing the sources and sinks of a given state variable [@Soetaert2008-er]. Forcing functions (or external variables) are external factors (i.e. not computed by the model) imposed (i.e. forced) to the model because they drive or regulate the system. Examples of forcing functions (among many others) in ecological models are light intensity (represented here by the solar radiation), temperature or wind. Finally, a model usually contains output variables (represented here by the Chlorophyll) that allow the comparison of the model to reality @Soetaert2008-er.

@@

Figure taken from [@Soetaert2008-er].
:::

@DeVries2017-wu and @Nowicki2022-no (panels e and f in @fig-export-ratios) are both data-assimilated models. These models operate by nudging model solutions to the observed fields (e.g. satellite and/or in situ data) or by optimizing model parameters to the observed fields [@Siegel2022-wd]. @DeVries2017-wu combined both satellite-derived data (NPP and PSS) and in situ observations (POC fluxes, DOC concentrations and dissolved $O_{2}$ distributions) to assess the carbon export and its transfer in the mesopelagic zone using a steady state ocean circulation inverse model (OCIM, the circulation component of their model). Their carbon export estimate is between 7.3 and 8.6 Pg C y$^{-1}$. @Nowicki2022-no added a two-phytoplankton/two-zooplankton food-web model with a migration zooplankton component to the model of @DeVries2017-wu in order to estimate the magnitude of each export pathway of the BCP. In all, @Nowicki2022-no estimated a carbon export of 10 Pg C y$^{-1}$.

@@

When we compare the $e-ratio$ maps (@fig-export-ratios) or the carbon export estimations of only six biogeochemical models (see @sec-biogeochem-models), we already observe strong differences. On the one hand, we are seeing an increase in model complexity from empirical models to data-assimilated inverse models. At the same time, we also gathered more observational data as well as a deeper understanding of the BCP (@sec-a-new-paradigm-for-the-bcp) that allows us to better represent its underlying processes. On the other hand, each degree of complexity inevitably accumulates more uncertainty due to the increasing number of processing and modeling steps (@fig-bgc-models).

@@

From the data we feed models with to uncertainties caused by missing or poorly misunderstood processes, current BCP models still disagree on the estimation of carbon export both currently and in response to climate change [@Henson2022-hg]. However, the ongoing increase in deployments of autonomous platforms and the development of new sensors is providing new opportunities to enhance the parametrization of key biogeochemical processes to better estimate carbon export and sequestration.

@@

## The potential of autonomous platforms {#sec-potential-autonomous-platforms}

@@

Remote sensing data acquired with ocean color satellites have been used for a long time [@Gordon1980-dm] to study key EZ variables related to carbon export [@Claustre2021-tx] such as phytoplankton biomass [@Robinson2004-cj], phytoplankton communities [@Uitz2015-hd] and particle size distribution [@Kostadinov2009-gf; @Kostadinov2010-bu] to name a few (see also @sec-biogeochem-models). While having a wide spatial coverage, these platforms are limited to the ocean's surface and their measures can be affected by several factors such as the cloud cover or low solar elevation (e.g. @Marshall1994-vk).

@@

## Specific sensors on autonomous platforms for the study of the BCP {#sec-BGC-sensors}

The BGC-Argo array (@sec-potential-autonomous-platforms) has already demonstrated its ability to understand some aspects of the BCP [e.g. @Lacour2017-ro; @Lacour2019-id; @Briggs2020-gz; @Yang2021-vg; @Llort2018-pa; @Wang2022-hn]. However, the current array may lack some key data to further our understanding of the BCP. Therefore, other types of sensors could be added to help fill this gap.

@@

![Illustration of an augmented BGC-Argo float. From top to bottom: GPS & Iridium (two-way communication) antenna, Oxygen optode, CTD (salinity, temperature and depth), pH sensor, radiometer (downwelling photosynthetic available radiation and downwelling irradiance at 380, 412 and 490 nm), fluorometer (Chla and colored dissolved organic matter) and scattering meter ($b_{bp}$), UVP6 (particle size spectra and images), transmissometer (particle beam attenuation) and nitrate sensor. \@Thomas Boniface.](image/ObservingCarbonCycle/float_picture1.png){#fig-bgc-float width="400"}

@@

$$
c = \frac{ln(T_{r})}{r}
$$ {#eq-bean-attenuation}

@@

The use of transmissometers to characterize POC concentrations was shown by @Bishop1999-es who found that POC concentrations were well correlated with $c_{p}$, independently of ocean environment, season or depth. Subsequently, the idea of using a transmissometer as an OST was firstly applied by @Bishop2004-at where the magnitude of carbon export was quantified based on the particles accumulation on the upward-facing window of vertically oriented transmissometers on autonomous floats while they were drifting (i.e. parked at a specific depth). This method was later improved by [@Estapa2013-gw] who divided the attenuation signal into a continuous component, that is the regular accumulation of small particles on the transmissometer window and a discontinuous component resulting in positive jumps likely attributed to the deposition of (rarer) large particles (see @fig-estapa-method and @sec-case-study-labrador-sea). @Estapa2017-jr further calibrated the OST carbon flux proxy using codeployed sediment traps and drifting transmissometers thus allowing the conversion of $c_{p}$ attenuation fluxes (units: m$^{-1}$d$^{-1}$) into carbon fluxes (units: mg C m$^{-2}$d$^{-1}$) using empirical POC-to-attenuance (ATN) ratio were ATN (unitless) is the product of $c_{p}$ and the transmissometer pathlength.

@@

jump_plot <- ggplot(tmp2, aes(x = dates, y = cp, fill = colour)) + geom_point(size= 3) +
  geom_point(data = jump, aes(x = dates, y = cp), size = 3, shape = 21) +
  #scale_fill_manual(values = c('#003366','#DCEEF3')) +
  scale_fill_manual(values = c('#DCEEF3', '#003366')) +
  theme_bw() +
  ylab(TeX('$c_{p}~(m^{-1})$')) +
  xlab('Datetime') +
  theme(legend.position = 'top', legend.title = element_blank())

@@

@Guidi2008-vp found an optimal couple of parameters $(A, B) = (12.5, 3.81)$ while @Iversen2010-an followed the same procedure and found $(A, B) = (273, 4.27)$ whereas @Fender2019-ou found $(A, B) = (15.4, 1.05)$. @Iversen2010-an assumed that the difference in the optimal couple of parameters was due to the study site used for the minimization (productive upwelling system versus open ocean in @Guidi2008-vp) while @Fender2019-ou suggested that a value of $B < 3$ means that either the density or sinking speed of particles is inversely correlated with particles diameter thus they suspected that the flux was dominated by particles in the lower size detection limit of the UVP they were using. Other values for $A$ and $B$ are being used in the literature [e.g. @Kiko2017-qy] based on a mechanistic approach developed by @Kriest2002-oc to investigate the formation of marine aggregates.

In all, it seems that the choice for the values of $A$ and $B$ is critical for deriving carbon fluxes derived from PSD [@Iversen2010-an; @Fender2019-ou]. Three main limitations highlighted by @Bisson2022-bt for UVP optically derived estimates of flux would be: (1) assuming that $A$ and $B$ are globally valid at all depths, for all UVP models and across all size classes, (2) the size to sinking rate uncertainty and (3) the size to carbon mass uncertainty..

@@

## Research questions and objectives

@@

This framework will hopefully address the questions raised so far, i.e., better understand the underlying drivers of each component of the BCP, decouple the contribution of each pump to the observed downward carbon flux lengthily attributed to the BGP and estimates of carbon sequestration [@Boyd2019-ez; @Passow2012-zh] as well as close the ocean carbon budget [@Burd2010-hc].

@@

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp-ia I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  4 BGC-Argo floats equipped with both a transmissometer and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 to investigate the post-spring bloom and its associated POC fluxes. In @sec-case-study-labrador-sea, I will show how transmissometers used as OSTs compare with PSDs measured by UVP6s as well as investigate the link between small and big particle fluxes derived by both instruments.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1000 m). In @sec-to-do, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.

>>>>

![$e-ratio$ estimations obtained with different types of models: empirical models (a, b), food-web models (c, d) and data-assimilated models (e, f). Note that the export value computed by @Laws2011-nw (9 Pg C year$^{-1}$) was recomputed by @Siegel2022-wd (6.9 Pg C year$^{-1}$), therefore the $e-ratio$ map presented here might not be representative of the one we would have got with the initial export value. Figure taken from @Siegel2022-wd.](image/ObservingCarbonCycle/export_ratio.jpeg){#fig-export-ratios}

@@

@Henson2011-mt and @Laws2011-nw (panels a and b in @fig-export-ratios) are both empirical models. @Henson2011-mt parameterized the $e-ratio$ as a decreasing function of sea surface temperature (SST, derived from satellite observations (see @fig-bgc-models)) tuned on a compilation of $^{234}Th$-derived export measurement (see @sec-historical-measurements) for a total export estimated at 5 Pg C year$^{-1}$. @Laws2011-nw modelled the $e-ratio$ as a decreasing linear function of SST and a power-law function of NPP whose parameters were determined using particle export estimates based on estimates of new production (nitrogen-based) and $^{234}Th$ and sediment trap export flux data compiled by @Dunne2005-an. They estimated a total export of 9 Pg C year$^{-1}$.

@Siegel2014-wg and @Archibald2019-dj (panels c and d in @fig-export-ratios) are both food-web models (see Information Box 3). @Siegel2014-wg used a mechanistic approach using satellite observations (NPP, PSS and phytoplankton carbon concentrations, see also @fig-bgc-models) to estimate the export of the BGP (6 Pg C year$^{-1}$). @Archibald2019-dj added a new module to the model of @Siegel2014-wg in order to incorporate the diel vertical migration of zooplankton for a total export of 6.5 Pg C year$^{-1}$.

@@

A simple food-web model is the NPZD model, which consists of four state variables: Nutrient (DIN), Phytoplankton (PHYTO), Zooplankton (ZOO) and DETRITUS. The arrows represent the flows (or interactions) between the state variables (e.g. f1 represents the DIN uptake by PHYTO, f2 represents the grazing of PHYTO by ZOO, etc.), describing the sources and sinks of a given state variable [@Soetaert2008-er]. Forcing functions (or external variables) are external factors (i.e. not computed by the model) imposed (i.e. forced) to the model because they drive or regulate the system. Examples of forcing functions (among many others) in ecological models are light intensity (represented here by the solar radiation), temperature or wind. Finally, a model usually contains output variables (represented here by the Chlorophyll) that allow the comparison of the model to reality [@Soetaert2008-er].

@@

Figure taken from @Soetaert2008-er.
:::

@DeVries2017-wu and @Nowicki2022-no (panels e and f in @fig-export-ratios) are both data-assimilated models. These models operate by nudging model solutions to the observed fields (e.g. satellite and/or in situ data) or by optimizing model parameters to the observed fields [@Siegel2022-wd]. @DeVries2017-wu combined both satellite-derived data (NPP and PSS) and in situ observations (POC fluxes, DOC concentrations and dissolved $O_{2}$ distributions) to assess the carbon export and its transfer in the mesopelagic zone using a steady state ocean circulation inverse model (i.e. the circulation component of their model). Their carbon export estimate range between 7.3 and 8.6 Pg C year$^{-1}$, depending on the selected export depth (i.e. respectively, 100 m and the euphotic depth). @Nowicki2022-no added a two-phytoplankton/two-zooplankton food-web model with a migration zooplankton component to the model of @DeVries2017-wu in order to estimate the magnitude of each export pathway of the BCP. In all, @Nowicki2022-no estimated a carbon export of 10 Pg C year$^{-1}$.

@@

When we compare the $e-ratio$ maps (@fig-export-ratios) or the carbon export estimations of only six biogeochemical models (see @sec-biogeochem-models), we already observe significant differences. On the one hand, we see an increase in model complexity from empirical models to data-assimilated inverse models thanks to the increase in the quantity and quality of observations as well as well as a deeper understanding of the BCP (@sec-a-new-paradigm-for-the-bcp). On the other hand, each degree of complexity inevitably accumulates more uncertainty due to the increasing number of processing and modeling steps (@fig-bgc-models).

@@

From the data we feed models with to uncertainties caused by missing or poorly understood processes, current BCP models still disagree on the estimation of carbon export both currently and in response to climate change [@Henson2022-hg]. However, the ongoing increase in deployments of autonomous platforms and the development of new sensors is providing new opportunities to enhance the parametrization of key biogeochemical processes to better estimate carbon export and sequestration.

@@

### The potential of autonomous platforms

@@

Remote sensing data acquired with ocean color satellites have been used for a long time [@Gordon1980-dm] to study key EZ variables related to carbon export [@Claustre2021-tx] such as phytoplankton biomass [@Robinson2004-cj], phytoplankton communities [@Uitz2015-hd] and particle size distribution [@Kostadinov2009-gf; @Kostadinov2010-bu] to name a few (see also @sec-biogeochem-models and @fig-bgc-models). While having a wide spatial coverage, these platforms are limited to the ocean's surface and their measures can be affected by several factors such as the cloud cover or low solar elevation (e.g. @Marshall1994-vk).

@@

### Specific sensors on autonomous platforms for the study of the BCP {#sec-BGC-sensors}

The BGC-Argo array has already demonstrated its ability to understand some aspects of the BCP [e.g. @Lacour2017-ro; @Lacour2019-id; @Briggs2020-gz; @Yang2021-vg; @Llort2018-pa; @Wang2022-hn]. However, the current array may lack some key data to further our understanding of the BCP. Therefore, other types of sensors could be added to help fill this gap.

@@

![Illustration of an augmented BGC-Argo float. From top to bottom: GPS & Iridium (two-way communication) antenna, Oxygen optode, CTD (salinity, temperature and depth), pH sensor, radiometer (downwelling photosynthetic available radiation and downwelling irradiance at 380, 412 and 490 nm), fluorometer (Chla and colored dissolved organic matter) and scattering meter ($b_{bp}$), underwater camera UVP6 (particle size spectra and images), transmissometer (particle beam attenuation) and nitrate sensor. \@Thomas Boniface.](image/ObservingCarbonCycle/float_picture1.png){#fig-bgc-float width="400"}

@@

$$
c = -\frac{ln(T_{r})}{r}
$$ {#eq-bean-attenuation}

@@

The use of transmissometers to characterize POC concentrations was shown by @Bishop1999-es who found that POC concentrations were well correlated with $c_{p}$, independently of ocean environment, season or depth. Subsequently, the idea of using a transmissometer as an OST was firstly applied by @Bishop2004-at where the magnitude of carbon export was quantified based on the particles accumulation on the upward-facing window of vertically oriented transmissometers on autonomous floats while they were drifting (i.e. parked at a specific depth). This method was later improved by [@Estapa2013-gw] who divided the attenuation signal into a continuous component, that is the regular accumulation of small particles on the transmissometer window and a discontinuous component resulting in positive jumps likely attributed to the deposition of (rarer) large particles (see @fig-estapa-method and @sec-case-study-labrador-sea). @Estapa2017-jr [-@Estapa2023-oz] further calibrated the OST carbon flux proxy using codeployed sediment traps and drifting transmissometers thus allowing the conversion of $c_{p}$ attenuation fluxes (units: m$^{-1}$d$^{-1}$) into carbon fluxes (units: mg C m$^{-2}$d$^{-1}$) using empirical POC-to-attenuance (ATN) ratio were ATN (unitless) is the product of $c_{p}$ and the transmissometer pathlength.

@@

jump_plot <- ggplot(tmp2, aes(x = dates, y = cp, fill = colour)) + geom_point(size= 3) +
  geom_point(data = jump, aes(x = dates, y = cp), size = 3, shape = 21) +
  #scale_fill_manual(values = c('#003366','#DCEEF3')) +
  scale_fill_manual(values = c('#DCEEF3', '#003366')) +
  theme_bw() +
  ylab(TeX('$c_{p}~(m^{-1})$')) +
  xlab('Date') +
  theme(legend.position = 'top', legend.title = element_blank())

@@

@Guidi2008-vp found an optimal couple of parameters $(A, B) = (12.5, 3.81)$ while @Iversen2010-an followed the same procedure and found $(A, B) = (273, 4.27)$ whereas @Fender2019-ou found $(A, B) = (15.4, 1.05)$. @Iversen2010-an assumed that the difference in the optimal couple of parameters was due to the study site used for the minimization (productive upwelling system versus open ocean in @Guidi2008-vp). @Fender2019-ou suggested that a value of $B < 3$ means that either the density or sinking speed of particles is inversely correlated with particles diameter thus they suspected that the flux was dominated by particles in the lower size detection limit of the UVP they were using. Other values for $A$ and $B$ are used in the literature [e.g. @Kiko2017-qy] based on a mechanistic approach developed by @Kriest2002-oc to investigate the formation of marine aggregates.

It seems that the choice for the values of $A$ and $B$ is critical for deriving realistic carbon fluxes estimations from PSD [@Iversen2010-an; @Fender2019-ou]. Three main limitations highlighted by @Bisson2022-bt for UVP optically derived estimates of flux would be: (1) assuming that $A$ and $B$ are globally valid at all depths, for all UVP models and across all size classes, (2) the size to sinking rate uncertainty and (3) the size to carbon mass uncertainty.

@@

## Research questions and objectives of this work

@@

This framework will hopefully address the key points raised so far, i.e., better understand the underlying drivers of each component of the BCP, decouple the contribution of each pump to the observed downward carbon flux lengthily attributed to the BGP and refine carbon export and sequestration estimates [@Boyd2019-ez; @Siegel2022-wd].

@@

1.  BGC-Argo floats equipped with a UVP6 and the zooplankton recognition algorithm are able to classify particles larger than 0.6 mm. However, these AUVs are limited in terms of their battery life. They are typically deployed for several years, which requires special attention to the energy consumption of each sensor. In @sec-uvp-ia, I will therefore describe the methodology used to develop the zooplankton classification model for the UVP6 accounting for energy limitations.
2.  Four BGC-Argo floats equipped with both a transmissometer and a UVP6 were deployed for the first time in the Labrador Sea in late May 2022 with the aim of observing POC export events due to the annual spring bloom. Unfortunately, it appears that the deployment occurred at the end of the spring bloom therefore we likely missed the major export events. In @sec-case-study-labrador-sea, I will therefore study the aftermaths of the spring bloom in terms of carbon fluxes estimated by both instruments. I will also compare the small (continuous) and big (stochastic) flux of particles as seen by transmissometers used as OSTs with PSDs measurements by UVP6s at three different drifting depths to investigate the relationship between the two instruments.
3.  Many studies have assumed that carbon sequestration only occurs in the deep ocean (typically 1000 m). In @sec-to-do, we reassess the global sequestration ($\geq$ 100 years) of the BCP and its components by using a continuous approach to carbon storage as opposed to the common view of long-term sequestration below a fixed reference depth.
